---
title: "MS4"
author: "Kiera O'Brien"
date: "3/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(haven)
library(tidyverse)
```

"About" section

Project Summary: This project is a data-driven analysis of Republican opinions on climate change. My thesis is on the right-wing climate movement from the 1980s to the present day. I'm particularly interested in examining the generational divide that exists with opinions on climate change policy. I'm still deciding which questions will be useful for my project and how best to utilize the demographic information. 

Data Sets: CCES 2010 Data and CCES 2018 Data. The Cooperative Congressional Election Study is run during election years and is a 50,000+ person national stratified sample survey administered by YouGov. I've selected these particular years because 2010 was the first year that the questionaire included a question regarding CO2 emission regulations directly, which is a metric I am interested in examining. 2018 is the most recent data collected, allowing for a change-over-time comparison. The data sets can be found online at: https://cces.gov.harvard.edu/.

About me: My name is Kiera O'Brien. I'm a senior in Harvard College studying Government on the Technology Science track. I was born and raised in Ketchikan, Alaska, and am the President Emerita of the Harvard Republican Club. 

I can be contacted at kiera_obrien@college.harvard.edu.
My github repo for this project can be found at: https://github.com/kieraeobrien/MS4

``` {r data, include = F}

# Note: each of these datasets comes with a guide for interpretation.
# It is on the CCES website. I used it to help select useful questions.
# https://cces.gov.harvard.edu/, under each year. 

# reading in Stata file of CCES 2010 data

cces_2010 <- read_dta("~/Documents/Harvard/2020 Spring/Thesis/CCES/cces_2010_common_validated.dta")

View(cces_2010)

# reading in Stata file of CCES 2018 data

cces_2018 <- read_dta("~/Downloads/cces18_common_vv.dta")

View(cces_2018)
```

``` {r 2010 questions, include = F}

# this block is for isolating potential questions within the 2010 dataset

# creating variable; Jobs versus Environment column in 2010 data

jve10 <- cces_2010$CC325
View(jve10)

```
``` {r 2018 questions, include = F}

# this block is for isolating potential questions within the 2018 dataset

# creating variable; agree/disagree with withdrawl from Paris Climate Agreement

paris18 <- cces_2018$CC18_332c
View(paris18)

# creating variable; should the EPA be able to regulate carbon emissions

carbonreg18 <- cces_2018$CC18_415a
View(carbonreg18)

# creating variable; on lowering fuel efficiency standards

fuelstand18 <- cces_2018$CC18_415b
View(fuelstand18)

# creating variable; requiring minimum renewable portfolios by states

renew18 <- cces_2018$CC18_415c
View(renew18)

# creating variable; strengthening EPA enforcement of Clean Air Act

enforce18 <- cces_2018$CC18_415d
View(enforce18)
```

